\section{SCENARIOS}
Here is the description of the possible scenarios.
\subsection{Scenario 1}
After having lunch with his friends, Johnny decides to not take the subway in order to get home. Instead he wants to benefit from the PowerEnJoy service he registered to the week before. 

He logs into the system through the mobile application he previously downloaded on his smartphone and, providing his credentials, he is able to find the location of the available cars near the restaurant. 

Since none of the cars is near enough, he closes the application without making any reservation. 
\subsection{Scenario 2}
Tonight Johnny has to attend a family dinner but, since he is late, he tells his sister, who was supposed to pick him up, to go ahead without him. 

Just before leaving his house, he realizes it is a public holiday and therefore there are no public transports available. In order to reach his family's house, he then decides to benefit from the PowerEnJoy service. 

He logs into the system website using his laptop and, providing his credentials, he manages to find an available car not far from his house. He reserves the car and, doing so, he is able to attend the family dinner only ten minutes late.
\subsection{Scenario 3}
After having dinner together, a group of friends decides to go see a movie. Johnny suggests to use the PowerEnJoy service even though none of them have ever registered to it. 

Having the smartphone with the best Internet connection, Jack offers to register. After downloading the mobile application, he fills out the registration form providing the required credentials and payment information. 

After receiving the password via email, he logs in for the first time and he is able to make a reservation. Once the destination is reached, Jack discovers with pleasure that he can benefit from a 10\% discount since he took two other passengers onto the car with him. 

Pleased with the service, the group decides to use it also to get back home.
\subsection{Scenario 4}
Laura, a British environmentalist tourist, decided to visit his friend Johnny in Milan. 

One night she tells him she would love to visit the city, so Johnny suggests her to register into the PowerEnJoy system he already used.

Since Laura is a bit reluctant, Johnny tries to convince her by showing her the service website and pointing out that all cars are electric. He also shows her where to keep track of the promotions and how to manage her personal information. 

Persuaded by her friend, Laura decides to register into the system the day after.
\subsection{Scenario 5}
After spending the afternoon at his university, Johnny decides to go visit his girlfriend whose house is forty minutes from him. 

He then chooses to use the PowerEnJoy service, aware that there are lots of safe areas near his girlfriend house. 

After logging into the system and reserving a car, he decides to bring her a gift and remembers that there is a florist next to his university. Once the flowers are chosen, he realizes that more than an hour has passed since his reservation. He takes his smartphone out of his pocket and realizes he received an email, saying that he has been charged with a 1EUR fee for not showing up in time and that the car he reserved is no more available. 

Aware of his mistake, he decides to not overthink it and starts searching for another available car. Once he finds it, he gets there immediately and starts driving to reach his girlfriend's house.
\subsection{Scenario 6}
After deciding to invite his friends over for lunch, Jack realizes there is nothing in the fridge and hurries to the grocery store. After leaving his house, he notices a PowerEnJoy car right in front of him and he chooses to use it instead of taking the bus. 

Once the car is reserved, Jack unlocks it and proceeds to the grocery store. After reaching his destination, he sadly realizes there are no free safe areas nearby and decides to leave the car in a generic parking lot, sure that it does not change anything. 

Once he is finished with the grocery shopping, he wants to reserve another PowerEnJoy car and, logging into the website, he finds out that his previous reservation has not yet ended. He then understands that the system stops charging the user only in the case the car is parked in a safe area. 

Finally Jack decides to head back home with that same car and sadly realizes he could have avoided to pay that much money. 
\subsection{Scenario 7}
After a long day at work, Dave realizes it is raining outside and does not want to walk back home. He then decides to benefit from the PowerEnJoy service, that he has been using for the last month and really appreciate. 

Sitting in the hall, Dave starts looking for a car on the mobile application and finally gets the results: there is a car parked a few blocks away and he decides to reserve it. 

After getting close enough to the car, he unlocks it and, getting in, realizes with surprise that the car monitor is broken. After spending a few minutes contemplating his options, Dave remembers that the service offers the possibility to report an issue and decides to go on with it. 

He then exits the car and decides to walk back home, for the first time in his life disappointed by the service.
\subsection{Scenario 8}
Every morning Alex goes to the university by bike in order to avoid air pollution. Class after class, it is finally time to head back home, but when Alex reaches the courtyard where she parked her bicycle, she realizes it is no longer there. It was stolen!! 

Upset by the fact, she decides to use the PowerEnJoy service to reach the nearest police station and report the theft. After logging into the system, she reserves a car not far from her and, after unlocking it, starts her ride. 

Once the police station is reached, Alex parks the car in a special safe area right in front of it. She then plugs the car into the power grid and happily sees on the monitor that a 30\% discount has been applied on the ride's total price.